---
title: "Car Fuel Efficiency Predictor"
author: "Ronald"
date: "23 Jan 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Aim

This project is to build a fuel efficiency predictor shiny app for cars.

The app is available at <https://ronaldyeo.shinyapps.io/Car_Fuel_Efficiency_Predictor/>

The github repository is available at
<https://github.com/ronaldyeo/Car-Fuel-Efficiency-Predictor/>


## Prediction Model Data Set

The app prediction model was built using the _mtcars_ data set. 

```{r, echo = TRUE}
head(mtcars)
```


## Prediction Model Building

As 1/4 mile time for cars are usually not available, it was removed from the feature for model building.  A stepwise algorithm by AIC was then performed to select the features for model building. 3 features, (i) no. of cylinders, (ii) gross horsepower, and (iii) weight were selected as the predictors for the regression model. A 10-fold cross validation of the regression model was conducted to test and score the model. 

```{r, echo = TRUE, eval = FALSE}
model <- lm(mpg ~ . -qsec, data = mtcars)
step(model)
control.par <- trainControl(method="cv", 10)
lm_model <- train(mpg ~ cyl + hp + wt, data=mtcars, method="lm",  trControl=control.par)
lm_model
```

The regression model has a Rsquared of **0.9052981**.

## Fuel Efficiency Predictor App

Input the 3 features,

(i) _no. of cylinders_, 
(ii) _gross horsepower_, and 
(iii) _weight_ 

of your car in the shiny app to predict your car fuel efficiency.
